### 2021-09-23 documentos/vector_space.tex
fixed conflicts (LOL merge -s ours; push -f)

The problem of determining complete positivity of a PCE can be recast as 
determining which vectors $\vec \tau$ are mapped via
$\san$
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:condition}
% \end{equation}
to a positive vector $\vec p$. In compontents, this would read 
\begin{equation}
\left(
\san_{\vec\alpha\vec\beta}
\right)
\tau_\beta=2^Np_{\vec\alpha}
\label{eq:4}
\end{equation}
where
$\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
\sa_{\alpha_N\beta_N}$. From the

It results convenient to express the 
previous equation in

We look for those vectors $\vec\tau$ consisting of 0's and 1's such that 
\begin{equation}
\san\vec\tau=2^N\vec p
\label{eq:3}
\end{equation}
where $\vec p$ is a vector with positive entries. Here $\vec\tau$ is a $4^N$ dimensional vector of 0's
and 1's. We number the entries of $\vec\tau$ 
by the multi-indices $\vec\alpha=(\alpha_1,\ldots,\alpha_N)$ where $0\leq\alpha_k\leq3$.
The entries of the positive vector are given by $2^Np_{\vec\alpha}$. It then follows that 
the expression (\ref{eq:3}) satisfies
\begin{equation}
\left(
\san_{\vec\alpha\vec\beta}
\right)
\tau_\beta=2^Np_{\vec\alpha}
\label{eq:4}
\end{equation}
where
\begin{equation}
\left(
\san_{\vec\alpha\vec\beta}
\right)=\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
\label{eq:5}
\end{equation}

From (\ref{eq:4}) immediately follows, via (\ref{eq:1})
\begin{equation}
\tau_\alpha=\left(
\san_{\vec\alpha\vec\beta}
\right)p_\beta
\label{eq:6}
\end{equation}
which we analyze iteratively. We shall essentially use the fact that
\begin{equation}
p_{\vec\alpha}+p_{\vec\beta}=0\quad\Leftrightarrow\quad p_{\vec\alpha}=p_{\vec\beta}=0
\label{eq:7}
\end{equation}

>>>>

% Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
The problem of determining complete positivity of a PCE can be recast as 
determining which vectors $\vec \tau$ are mapped via
$\san$
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:condition}
% \end{equation}
to a positive vector $\vec p$. In compontents, this would read 
\begin{equation}
% \left(
\san_{\vec\alpha\vec\beta} \,
% \right)
\tau_\beta=2^Np_{\vec\alpha}
\label{eq:A:tau:is:p}
\end{equation}
where
$\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
\sa_{\alpha_N\beta_N}$. Using the fact that $a=a^{-1/2}$ (so
$A = A^{-1}/2^N$) we can directly invert \eref{eq:A:tau:is:p} 
and obtain 
\begin{equation}
\tau_\alpha=
% \left(
\san_{\vec\alpha\vec\beta} \,
% \right)
p_\beta,
\label{eq:tau:is:A:p}
\end{equation}
which will serve as a starting point for our analysis. Other simple but crucial
observation that we shall use is that, for valid quantum channels, 
$p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
all $p_{\vec\alpha} \ge 0$ due to 
complete positivity of the underlying channel.

% We shall essentially use the fact that
% 
% 
% 
% It results convenient to express the 
% previous equation in  
%

% We look for those vectors $\vec\tau$ consisting of 0's and 1's such that 
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:3}
% \end{equation}
% where $\vec p$ is a vector with positive entries. Here $\vec\tau$ is a $4^N$ dimensional vector of 0's
% and 1's. We number the entries of $\vec\tau$ 
% by the multi-indices $\vec\alpha=(\alpha_1,\ldots,\alpha_N)$ where $0\leq\alpha_k\leq3$.
% The entries of the positive vector are given by $2^Np_{\vec\alpha}$. It then follows that 
% the expression (\ref{eq:3}) satisfies
% \begin{equation}
% \left(
% \san_{\vec\alpha\vec\beta}
% \right)
% \tau_\beta=2^Np_{\vec\alpha}
% \label{eq:4}
% \end{equation}
% where
% \begin{equation}
% \left(
% \san_{\vec\alpha\vec\beta}
% \right)=\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% \label{eq:5}
% \end{equation}
% 
% From (\ref{eq:4}) immediately follows, via (\ref{eq:1})
% \begin{equation}
% \tau_\alpha=\left(
% \san_{\vec\alpha\vec\beta}
% \right)p_\beta
% \label{eq:6}
% \end{equation}
% which we analyze iteratively. We shall essentially use the fact that
% \begin{equation}
% p_{\vec\alpha}+p_{\vec\beta}=0\quad\Leftrightarrow\quad p_{\vec\alpha}=p_{\vec\beta}=0
% \label{eq:7}
% \end{equation}
% }}}
